---
output:
  pdf_document: default
  html_document: default
---

IT344-F19
Jack Luu


#1.	Write an example of a rule with high confidence? 

In rhs ‘other vegetables’, the highest confidence is {citrus fruit,root vegetables}

In rhs ‘whole milk’, the highest confidence is {curd,yogurt}    



#2.	Write an example of a rule with high lift?

In rhs ‘other vegetables’, the highest lift is rule {citrus fruit,root vegetables}        

In rhs ‘whole milk’, the highest lift is rule {curd,yogurt}                         


#3.	Which one will you pick if you were to choose product shelving decision in a grocery store? 

I will pick the rule with high lift and high confidence, with the focus on lift. 

Why? Because some rule have high confidence but low lift. 
Lift gives us information about the increase in probability of the consequent given the if antecedent part.


#R Code

```{r}
library(arules)
library(arulesViz)
```

```{r}
data ("Groceries")
class(Groceries)
```

```{r}
inspect(head(Groceries))
```

```{r}
myRules<-apriori(Groceries, parameter=list (support=0.01, confidence=0.5))
inspect(myRules)

```
```{r}
inspect (head(sort(myRules, by="confidence"), 3))
```
```{r}
wholemilkRules <- apriori(data=Groceries, parameter=list (supp=0.001,conf = 0.08), appearance = list (rhs="whole milk"))
```
```{r}
mySortedRules<-sort(myRules, by="lift")
inspect(mySortedRules)

```


