---
output:
  word_document: default
  html_document: default
---
Beige Book Quiz


```{r}
library(tidyverse)
exfile <- "http://www.itk.ilstu.edu/faculty/jrwolf/redwhite.csv"

df <- read_csv(exfile)
```

```{r}
df1 <- gather(df, key="measure", value="value", c("Red", "White"))

df1

```

```{r}
ggplot(df1, aes(x=Pips, y=value))+
  geom_bar(stat='identity', fill="dark blue")+
  facet_wrap(~measure)
```


```{r}
library(dplyr)

dfRed = df %>%
  select(Pips, Red)


dfWhite = df %>%
  select(Pips, White)

```

```{r}

dfRed$Red %>% chisq.test()

```

```{r}
dfWhite$White %>% chisq.test()
```



A chi-square test was performed to examine null hypthesis (HO) that the red dice is a fair dice which has the same probability of landing facing up (1/6). The results showed that p value < 0.05, df=5 (p < 2.2e-16) so the null hypothesis is rejected which means that the red dice is not a fair dice.  

A chi-square test was performed to examine null hypthesis (HO) that the white dice is a fair dice which has the same probability of landing facing up (1/6). The results showed that p value < 0.05, df=5 (p < 2.2e-16) so the null hypothesis is rejected which means that the white dice is not a fair dice.  
