---
output:
  pdf_document: default
  html_document: default
---




1. Formulate your question: draw a graph the looks the same as the one that shown.


2. Read in your data: checked

3. Check the packaging: checked

4. Run str(): checked

5. Look at the top and the bottom of your data: checked 

6. Check your “n”s: checked

7. Validate with at least one external data source: checked

8. Try the easy solution first: checked
9. Challenge your solution: checked
10. Follow up: checked


```{r}
library(tidyverse)
tips<-read_csv("https://raw.githubusercontent.com/mwaskom/seaborn-data/master/tips.csv")

str(tips)
cols(
  total_bill = col_double(),
  tip = col_double(),
  sex = col_character(),
  smoker = col_character(),
  day = col_character(),
  time = col_character(),
  size = col_integer()
  )

head(tips, 5)
tail(tips,5)


```
```{r}
nrow(tips)
```


```{r}
require(ggplot2)
jack <- ggplot(tips, aes(x = total_bill, y = tip)) + geom_point(aes(color = tips$`time`), shape = 1) + geom_smooth()
jack + xlab("Toatl Bill") + ylab("Tip")   
 
```


