---
title: "R Notebook"
output:
  pdf_document: default
  html_notebook: default
  word_document: default
  html_document:
    df_print: paged
---

1. Below is a link to a file listing the number women software engineers at several
Silicon Valley tech firms.
http://www.itk.ilstu.edu/faculty/jrwolf/wit.csv



```{r}
df <- read.csv("http://www.itk.ilstu.edu/faculty/jrwolf/wit.csv", 
                 header = TRUE)

head(df)
```



a. Create the R code to find the number women software engineers at Reddit.

```{r}
indexOfReddit <- which(df=="reddit")

womenOfReddit=df[indexOfReddit,4]

print(womenOfReddit)

```


b. Using the same link, create the R code to find the total number women software
engineers in the dataset.
```{r}

sum(df$num_female_eng)

```

2. If you run the R code below, it will create a dataframe (named pop) with 139
observations and 4 variables.

```{r}
### Start pop Code#######
install.packages("rvest")
library("rvest")
html <- read_html("https://www.ssa.gov/oact/babynames/numberUSbirths.html")
usBirthData <- html_table(html, fill=TRUE)
pop <- usBirthData[[1]]
pop$Male <- as.numeric(gsub(",", "", pop$Male))
pop$Female <- as.numeric(gsub(",", "", pop$Female))
pop$Total <- as.numeric(gsub(",", "", pop$Total))
names(pop) <- c("year", "male", "female", "total")
### End pop Code #######
```

a. Create the R code to find the year with the most children born.
```{r}
pop[which.max(pop$total),1]
```

b. Using the same list, create the R code to find the year with the fewest children born.
```{r}
pop[which.min(pop$total),1]
```





```{r}
topCities <-
read_html("https://en.wikipedia.org/wiki/List_of_cities_proper_by_population"
)
topCities <- html_table(
 html_node(
 topCities, "table.sortable"
 ), header=TRUE, trim=TRUE
)
names(topCities) <- c(
 "Rank", "City", "Image", "Population", "Definition",
 "Total.Area", "Population.Density", "Country"
)
topCities$Image <- NULL
topCities$Population <- as.numeric(
 gsub(",", "",
 gsub("^[0-9]+[^0-9]([0-9\\.,]+).*$", "\\1",
topCities$Population)
 )
)
topCities$Definition <- gsub("^([^\\[]+).*$", "\\1", topCities$Definition)
topCities$Total.Area <- as.numeric(
 gsub(",", "",
 gsub("^[0-9]+[^0-9]([0-9\\.,]+).*$", "\\1",
topCities$Total.Area)
 )
)
topCities$Population.Density <- as.numeric(gsub(",", "",
topCities$Population.Density))
```

a. Use the topCities dataframe and create the R code to find the 5 largest cities in
India


```{r}
allIndiaCities = topCities[which(grepl("India", topCities$Country)), ]

allIndiaCities[order(allIndiaCities$Rank),] 

print(allIndiaCities[1:5,1:2])
```

b. Use the topCities dataframe and create the R code to find the 5 largest cities in
China.

```{r}
allChinaCities = topCities[which(grepl("China", topCities$Country)), ]

allIndiaCities[order(allChinaCities$Rank),] 

print(allChinaCities[1:5,1:2])
```

