---
output:
  pdf_document: default
  html_document: default
---
```{r}
library(tidyverse)
```


# a. Reading in the data (R code given)
```{r}


Input =("
Program                            Student  WPM
'Dance Mat Typing'      a        35
'Dance Mat Typing'      b        50
'Dance Mat Typing'      c        55
'Dance Mat Typing'      d        60
'Dance Mat Typing'      e        65
'Dance Mat Typing'      f        60
'Dance Mat Typing'      g        70
'Dance Mat Typing'      h        55
'Dance Mat Typing'      i        45
'Dance Mat Typing'      j        55
'Dance Mat Typing'      k        60
'Dance Mat Typing'      l        45
'Dance Mat Typing'      m        65
'Dance Mat Typing'      n        55
'Dance Mat Typing'      o        50
'Dance Mat Typing'      p        60
'TypingClub'               q        55
'TypingClub'               r        60
'TypingClub'               s        75
'TypingClub'               t        65
'TypingClub'               u        60
'TypingClub'               v        70
'TypingClub'               w        75
'TypingClub'               x        70
'TypingClub'               y        65
'TypingClub'               z        72
'TypingClub'               aa       73
'TypingClub'               ab       65
'TypingClub'               ac       80
'TypingClub'               ad       50
'TypingClub'               ae       55
'TypingClub'               af       70
"
)

Data = read.table(textConnection(Input),header=TRUE)

```




# b. Examine the data (look at head and tail)

```{r}
head(Data)
tail(Data)
```


# c. Examine the structure (str) of the data
```{r}
str(Data)
```


# d. Find the Mean (mean) and Standard Deviation (sd) by Program of the data

```{r}
library(tidyverse)
Data%>%group_by(Program)%>% summarize(Program_mean = mean(WPM))
```
```{r}
Data%>% group_by(Program) %>%  summarize(Program_sd = sd(WPM))
```


# e. Create a botplot of the data (by Program)

```{r}
ggplot(Data, aes(Program,WPM)) + geom_boxplot()
```


# f. Create a histogram of the data (by Program)
```{r}
jack = ggplot(Data, aes(WPM)) + geom_histogram(fill="lightblue",breaks = seq(30,80, by=10)) +facet_wrap(~Program) +theme_classic()

jack
```
# g. Run a t-test on the data
```{r}

ind.t.test<-t.test(WPM ~ Program, data = Data)

ind.t.test
```



# h. report your findings using APA format 

#The 16 students who participated in the TypingClub #(M=66, #SD=8.41) compared to the 16 students in the #Dance Mat #Typing group(M=55, SD=8.84) demonstrated #significantly #better typing speed t(29) = -3.583, p=0.001.

```{r}
nrow(Data)
```




 