---
Student: Jack Luu
output: word_document
---

```{r}
df <- read.csv("http://www.itk.ilstu.edu/faculty/jrwolf/wit.csv", header = TRUE)
head(df)
```

---Question 1--------------


a. Create the R code to find the number women software engineers at Reddit.

```{r}
library(tidyverse)
x= filter(df, df$company == 'Reddit')
x$num_female_eng
```


b. Using the same link, create the R code to find the total number women software
engineers in the dataset.
```{r}
sum(df$num_female_eng)
```


--Question 2------------

2. If you run the R code below, it will create a dataframe (named pop) with 139
observations and 4 variables.

```{r}
### Start pop Code#######
library(tidyverse)
library("rvest")
html <- read_html("https://www.ssa.gov/oact/babynames/numberUSbirths.html")
usBirthData <- html_table(html, fill=TRUE)
pop <- usBirthData[[1]]
pop$Male <- as.numeric(gsub(",", "", pop$Male))
pop$Female <- as.numeric(gsub(",", "", pop$Female))
pop$Total <- as.numeric(gsub(",", "", pop$Total))
names(pop) <- c("year", "male", "female", "total")
### End pop Code #######
```

a. Create the R code to find the year with the most children born.
```{r}
pop[which.max(pop$total),1]
```

b. Using the same list, create the R code to find the year with the fewest children born.
```{r}
pop[which.min(pop$total),1]
```



--Question 3------------------

```{r}
topCities <-
read_html("https://en.wikipedia.org/wiki/List_of_cities_proper_by_population"
)
topCities <- html_table(
 html_node(
 topCities, "table.sortable"
 ), header=TRUE, trim=TRUE
)
names(topCities) <- c(
 "Rank", "City", "Image", "Population", "Definition",
 "Total.Area", "Population.Density", "Country"
)
topCities$Image <- NULL
topCities$Population <- as.numeric(
 gsub(",", "",
 gsub("^[0-9]+[^0-9]([0-9\\.,]+).*$", "\\1",
topCities$Population)
 )
)
topCities$Definition <- gsub("^([^\\[]+).*$", "\\1", topCities$Definition)
topCities$Total.Area <- as.numeric(
 gsub(",", "",
 gsub("^[0-9]+[^0-9]([0-9\\.,]+).*$", "\\1",
topCities$Total.Area)
 )
)
topCities$Population.Density <- as.numeric(gsub(",", "",
topCities$Population.Density))

head(topCities)
```

a. Use the topCities dataframe and create the R code to find the 5 largest cities in
India


```{r}
#Option 1
allIndiaCities = topCities[which(grepl("India", topCities$Country)), ]

#largest by "Rank"
allIndiaCities[order(allIndiaCities$Rank),] 
print(allIndiaCities[1:5,1:2])

```
```{r}
#Option 2

#largest by "Rank"
IndiaCities= filter(topCities, Country=="India")
IndiaCities[order(IndiaCities$Rank),] 
print(IndiaCities[1:5,1:2])
```


b. Use the topCities dataframe and create the R code to find the 5 largest cities in
China.

```{r}
##Option 1:
#largest by "Rank"
allChinaCities = topCities[which(grepl("China", topCities$Country)), ]
allChinaCities[order(allChinaCities$Rank),] 
allChinaCities[1:5,1:2]


#Option 2:
#largest by "Rank"
ChinaCities= filter(topCities, Country=="China")
ChinaCities[order(allChinaCities$Rank),] 
ChinaCities[1:5,1:2]

```

--Question 4-----------------

```{r}


library(magrittr) # needs to be run every time you start R and want to use %>%
library(dplyr)    # alternatively, this also loads %>%
url =  "https://en.wikipedia.org/wiki/List_of_S%26P_500_companies"
url %>%
 read_html() %>%
 html_nodes("#constituents") %>%
 html_table(header = T) -> sp500
sp500 <- sp500[[1]]
names(sp500) <- c(
 "Ticker", "Name", "SEC.Filing", "GICS.Sector",
 "GICS.SubIndustry", "Location.HQ", "Date.Added", "CIK", "Founded")

sp500$Date.Added <- as.numeric(substr(sp500$Date.Added,1,4))
```


```{r}
head(sp500)
```

a. Create the R code to find the names of firms added to the S&P 500 since
2010.

```{r}
companySince2010 = filter(sp500, Date.Added>=2010)

head(companySince2010[, c(2,7)])
```

b. Create the R code to find the total number of firms in the table.

```{r}
nrow(sp500)
```




--Question 5-------------------

5. According to Wikipedia: "The 2015 Cricket World Cup was the 11th Cricket World
Cup, jointly hosted by Australia and New Zealand. Fourteen teams played 49 matches
in 14 venues.


```{r}
### Start Venue R Code ####
cricket_world_cup <-
read_html("http://en.wikipedia.org/wiki/2015_Cricket_World_Cup")
venues = html_table(html_nodes(cricket_world_cup, "table")[[5]])
### End Venue R Code ####

```


a. Use the venue dataframe to find the name of the venue with the largest capacity.

```{r}
venues$Capacity = as.numeric(gsub(",","",venues$Capacity))
filter(venues,  Capacity== max(venues$Capacity))
```

b. Use the venue dataframe to find the name of the venue with the smallest
capacity.
```{r}
filter(venues,  Capacity== min(venues$Capacity))
```
