---
output:
  word_document: default
  html_document: default
---
```{r}
library(tidyverse)
exfile <- "http://www.itk.ilstu.edu/faculty/jrwolf/ebay.csv"
df <- read_csv(exfile)
```

# b. Examine the data (look at head and tail)

```{r}
head(df)
tail(df)
```

# c. Examine the structure (str) of the data
```{r}
str(df)
```

# d1. Find the Mean (mean) and Standard Deviation (sd) by old/new of Price

```{r}
df %>% group_by(Cond) %>% summarize(Mean = mean(Price))

df %>% group_by(Cond) %>% summarize(Standard_Dev = sd(Price))
```


# d2. Find the Mean (mean) and Standard Deviation (sd) by male/female of Price

```{r}
df %>% group_by(Gender) %>% summarize(Mean = mean(Price))

df %>% group_by(Gender) %>% summarize(Standard_Dev = sd(Price))

#summary(df)
```

# e1. Create a boxplot of Price (by old/new)
```{r}
p <- ggplot(df, aes(x=Cond, y=Price)) + geom_boxplot()
p
```

# e2. Create a boxplot of Price (by male/female)
```{r}
p1 <- ggplot(df, aes(x=Gender, y=Price)) + geom_boxplot()
p1
```


# f. Create a histogram of Price (by color)
```{r}
p2 <- ggplot(df, aes(x=Color, y=Price))+
  geom_histogram(stat='identity', color="dark blue")
p2
```


# g1. Run a t-test on Price (by old/new)
```{r}
ind.t.test<-t.test(Price ~ Cond, data = df)

ind.t.test
```


# g2. Run a t-test on Price (by male/female)
```{r}
ind.t.test<-t.test(Price ~ Gender, data = df)

ind.t.test
```


# h. report your findings for both t-tests using APA format (https://www.socscistatistics.com/tutorials/ttest/default.aspx)

##A t-test on Price by old/new
 
The old products (M=31.4, SD=11.1) compared to the new products (M= 42.7, SD = 8.7) demonstrated significantly lower price scores, t(790.57) = 17.91 ,p < 2.2e-16

There was no significant effect for sex, t(1044) = 0.945, p = 0.3448, despite women (M = 38.48,SD = 10.33) paying more than men (M = 37.83, SD = 12.20).

 