---
output:
  pdf_document: default
  html_document: default
---
# a. Reading in the data (R code given)

```{r}
library(tidyverse)

exfile <- "http://www.itk.ilstu.edu/faculty/jrwolf/ssl.csv"
df <- read_csv(exfile)
```
# b. Examine the data (look at head and tail)

```{r}
head(df)
tail(df)
```
# c. Examine the structure (str) of the data

```{r}
str(df)

```

# d1. Find the Mean (mean) and Standard Deviation (sd) by NSA of SSL
```{r}
df %>% 
  group_by(nsa) %>% 
  summarize(ssl_sd = sd(ssl))
```

```{r}
df %>% 
  group_by(nsa) %>% 
  summarize(ssl_mean = mean(ssl))
```
# d2. Find the Mean (mean) and Standard Deviation (sd) by paper of SSL
```{r}
df %>% 
  group_by(paper) %>% 
  summarize(ssl_sd = sd(ssl))
```

```{r}
df %>% 
  group_by(paper) %>% 
  summarize(ssl_sd = mean(ssl))
```







# e1. Create a boxplot of SSL (by NSA )

```{r}
ggplot(df, aes(nsa, ssl, group=nsa)) +
geom_boxplot(aes())
```
# e2. Create a boxplot of SSL (by paper )

```{r}
ggplot(df, aes(paper, ssl, group=paper)) +

  geom_boxplot(aes())
```


# f. Create a histogram of SSL (by NSA)
```{r}

ggplot(df, aes(ssl)) +
geom_histogram(fill="lightblue", color="blue",
breaks=seq(0,5,1))+
facet_wrap(~nsa)
```



# f. Create a histogram of SSL (by paper)
```{r}

ggplot(df, aes(ssl)) +
geom_histogram(fill="lightblue", color="blue",
breaks=seq(0,5,1))+
facet_wrap(~paper)
```


# g1. Run a t-test on SSL (by NSA)

```{r}
ind.t.test<-t.test(ssl ~ nsa, data = df)

ind.t.test
```



The 112 schools with NSA COE designation (M=3.56, SD=1.49) did not have significantly higher SSL Test scores compared to the 479 schools w/o a NSA COE designation (M=3.49, SD=1.57), t(173.94) = -0.48186, p=0.063.

# g2. Run a t-test on SSL (by paper)


```{r}
ind.t.test<-t.test(ssl ~ paper, data = df)

ind.t.test
```
# h. report your findings for both t-tests using APA format (https://www.socscistatistics.com/tutorials/ttest/default.aspx)

The 62 schools who were strong in research (M=3.82, SD=1.41) did not have significantly higher SSL Test scores compared to the 529 schools w/o a paper accepted at the ACM and IEEE conferences (M=3.46, SD=1.57), t(79.859) = -1.877, p=0.064.

